Global patterns of forest autotrophic carbon fluxes

### 2020-12-18 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

Our analysis clarifies how annual forest autotrophic C fluxes vary with latitude and climate on a global scale. 
To the extent that patterns across broad scale climatic gradients can foretell ecosystem responses to climate change, our findings suggest that higher temperatures with similar moisture availability would result in a generalized acceleration of forest C cycling (Figs. 2-3).
This is consistent with observations of continental- to global-scale increases over time in $GPP$ [@li_mapping_2019], $ANPP_{stem}$ [@brienen_long-term_2015; @hubau_asynchronous_2020], tree mortality [@brienen_long-term_2015; @mcdowell_drivers_2018], soil respiration [@bond-lamberty_global_2010], and heterotrophic soil respiration [@bond-lamberty_globally_2018]. 
However, increasing C flux rates are by no means universal [e.g., @rutishauser_testing_2020; @hubau_asynchronous_2020], likely because other factors are at play, including changes to other aspects of climate, atmospheric pollution (CO~2~, SO~2~, NO~x~), and local disturbances.
Moreover, forest ecosystem responses to climatic changes outside the temperature range to which forest communities are adapted and acclimatized will not necessarily parallel responses across geographic gradients in climate (**REF**).
Indeed, tree-ring studies from forests around the world indicate that tree growth rates -- along with $ANPP_{stem}$ and possibly other ecosystem C fluxes -- respond negatively to growing season temperature [e.g., @helcoski_growing_2019; @vlam_temperature_2014; @martin-benito_convergence_2015; @klesse_combined_2018].
Furthermore, in the tropics, climate change will push temperatures beyond any contemporary climate, and there are some indications that this could reduce forest C flux rates  [@mau_temperate_2018; @sullivan_long-term_2020] if paralleled by $VPD$ increases [@smith_empirical_2020].
Further research is required to understand the extent to which forest responses to climate change will track the observed global gradients, and the time scale on which they will do so.
In the meantime, understanding the fundamental climatic controls on annual C cycling in Earth's forests sets a firmer foundation for understanding forest C cycle responses to accelerating climate change.

>>>>

Our analysis clarifies how annual forest autotrophic C fluxes vary with latitude and climate on a global scale. 
To the extent that patterns across broad scale climatic gradients can foretell ecosystem responses to climate change, our findings suggest that higher temperatures with similar moisture availability would result in a generalized acceleration of forest C cycling (Figs. 2-3).
This is consistent with observations of continental- to global-scale increases over time in $GPP$ [@li_mapping_2019], $ANPP_{stem}$ [@brienen_long-term_2015; @hubau_asynchronous_2020], tree mortality [@brienen_long-term_2015; @mcdowell_drivers_2018], soil respiration [@bond-lamberty_global_2010], and heterotrophic soil respiration [@bond-lamberty_globally_2018]. 
However, increasing C flux rates are by no means universal [e.g., @rutishauser_testing_2020; @hubau_asynchronous_2020], likely because other factors are at play, including changes to other aspects of climate, atmospheric pollution (CO~2~, SO~2~, NO~x~), and local disturbances.
Moreover, forest ecosystem responses to climatic changes outside the temperature range to which forest communities are adapted and acclimatized will not necessarily parallel responses across geographic gradients in climate (**REF**).
Indeed, tree-ring studies from forests around the world indicate that tree growth rates -- along with $ANPP_{stem}$ and possibly other ecosystem C fluxes -- often respond negatively to growing season temperature, particularly in warmer climates [e.g., @helcoski_growing_2019; @vlam_temperature_2014; @martin-benito_convergence_2015; @klesse_combined_2018].
Furthermore, in the tropics, climate change will push temperatures beyond any contemporary climate, and there are some indications that this could reduce forest C flux rates  [@mau_temperate_2018; @sullivan_long-term_2020] if paralleled by $VPD$ increases [@smith_empirical_2020].
Further research is required to understand the extent to which forest responses to climate change will track the observed global gradients, and the time scale on which they will do so.
In the meantime, understanding the fundamental climatic controls on annual C cycling in Earth's forests sets a firmer foundation for understanding forest C cycle responses to accelerating climate change.
